Data_visualization

### 2018-09-06 Rmd/Data_visualization_common_names.Rmd
Data_preparation

```{r echo=FALSE, out.width='80%', fig.align='center'}
knitr::include_graphics('Images/all_species.png')
```

\newpage
```{r, message=FALSE, warning=FALSE, echo=FALSE,fig.width=8}
pollen_ratios_brassicaceae <- read.csv("Data/pollen_ratios_brassicaceae.csv", header = T)
ggplot(pollen_ratios_brassicaceae, aes(x=spp, y=ratio, fill=variable)) +
  geom_bar(stat='identity', position='dodge') +labs(title="Brassicaceae", x="", y="Pollen mix ratio") + 
  theme(axis.text.x=element_text(angle=60,hjust=1))+geom_hline(yintercept = 50)+
  scale_fill_manual(values=c("grey10", "grey60"))+ ylim(0,100)

@@

\newpage
```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3}
library(ggplot2)

>>>>

\newpage
#CHOLOROPLAST RBCL PHYLOGENY
```{r echo=FALSE, out.width='80%', fig.align='center'}
knitr::include_graphics('Images/all_species.png')
```

\newpage
###POLLEN MIX RATIOS PER FAMILY -3 NEXT PAGES-
```{r, message=FALSE, warning=FALSE, echo=FALSE,fig.width=8}
pollen_ratios_brassicaceae <- read.csv("Data/pollen_ratios_brassicaceae.csv", header = T)
ggplot(pollen_ratios_brassicaceae, aes(x=spp, y=ratio, fill=variable)) +
  geom_bar(stat='identity', position='dodge') +labs(title="Brassicaceae", x="", y="Pollen mix ratio") + 
  theme(axis.text.x=element_text(angle=60,hjust=1))+geom_hline(yintercept = 50)+
  scale_fill_manual(values=c("grey10", "grey60"))+ ylim(0,100)

@@

\newpage
###POLLEN PER ANTHER
```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3}
library(ggplot2)
